---
title: "Lab 1 - Data visualization"
author: "Miranda Zhong"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
library(tidyverse)
library(viridis)
```

## Exercise 1

```{r ex-1}
glimpse(midwest)
ggplot(midwest,
       aes(x= popdensity)) + geom_histogram(binwidth = 10000) + labs(title= "population density number", x = "population density", y = "count")
```
As shown in the graph, the distribution of the graph skew to the right. Althoguh most county have population density below 25000, there are some outliers which population locates between 50000 and 75000. 

## Exercise 2

```{r ex-2}
ggplot(midwest,
       aes(x=percollege, y= percbelowpoverty, color= state))+ geom_point()+scale_color_viridis_d()+ labs(title= "college percentage vs percentage below poverty", x = "college percentage", y = "percentage below poverty")
```


## Exercise 3
Most state have very similar college percentage, clustered around 10-20% with 10-20% below the poverty line. This means the amount of population that revieves college degree is roughly the same as the amount of people in poverty. 


## Exercise 4


## Exercise 5

boxplot area vs state

## Exercise 6

```{r}
midwest <- midwest |>
  mutate(metro = if_else(inmetro == 1, "Yes", "No"))

```
google what is a segmented bar chart


## Exercise 7
